---
title: "Tidy Tuesday Template"
author: "You!"
date: "3/26/2020"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Install the needed packages

You'll need to install both `remotes` and `tidytuesdayR` to do this:

```{r}
install.packages("remotes")
remotes::install_github("thebioengineer/tidytuesdayR")
#optional
#remotes::install_github("laderast/burro")
```

# Look at the available datasets

```{r}
library(tidytuesdayR)
#This will open up in the help window
tidytuesdayR::tt_available()
```

# What was your dataset?

Load your dataset in with the function below. The input is the date the dataset was issued. You should be able to get this from the `tt_available()` function.

```{r}
#incoming data comes in as a list
datasets <- tidytuesdayR::tt_load("2020-01-14")
#show the names of the individual datasets
names(datasets)
dataset <- datasets$passwords
```

A quick way to explore the data is with `burro`:

```{r}
burro::explore_data(dataset,outcome_var = NULL)
```

# What was your question?

Given your inital exploration of the data, was was the question you wanted to answer?

# What were your findings?

Put your findings and your visualization code here.

```{r}

```

# What did you learn?

Were there any lessons you learned? Any cool packages you want to talk about?
